---
title: "RShiny - A Web App"
subtitle: "A small introduction to RShiny."  
author: 
  - "Suhas P K"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE,
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

## Shiny Web app

- Shiny is a very powerful framework for building web applications based on R. 

- Shiny apps are easy to write. Let users interact with your data and your analysis, all with R or Python.

- Using `library(shiny)`, this will be an amateur attempt to create small functional web application.

---

## Overview

- This is a final project from **Johns Hopkins Data Science Specialization: Developing Data Products**.

- This assignment consists of two parts

- Part 1 : A Shiny application.
  1. A well documented user friendly Shiny application
  2. Deploying the application on Rstudio's shiny server.
  3. It must consist of an `input widget` (textbox, radio button, checkbox, ...) and operation on the UI input in server.R file.
  4. A reactive display as the result of the server calculation.

- Part 2 : A Reproducible Pitch Presentation.
  1. It must consists of 5 slides to pitch the idea done in the Slidify or Rstudio Presenter.
  2. The presentation should be pushed to github or Rpubs.
  3. It must be hosted on github pages or Rpubs.

---
## Implementation and Visualization

- Diamond data set is part of `library(ggplot2)` available in the R is used for this project.

- Based on the input given in the Shiny web application from the data set, a reactive plot is generated.

- The link to web app. CLICK ME!

---
## The Diamonds data set

```{r data , echo=FALSE, message=FALSE}
if (!require(ggplot2)){
  install.packages("ggplot2")
  library(ggplot2)
}
```

```{r eval=requireNamespace("DT", quietly=TRUE), message=FALSE}
DT::datatable(head(diamonds), fillContainer = FALSE, options = list(pageLength = 6))
```
---
### `summary` of Diamonds data set
```{r summary, message=FALSE, comment=""}
summary(diamonds)
```
---
class: inverse, center, middle
# Thank you!